# Correlation

```{r message = FALSE, warning = FALSE}
# Load packages
library(tidyverse)
library(plyr)
library(dplyr)
library(tsibble)
library(ggplot2)
library(feasts)
library(lubridate)
library(GGally)
```


```{r}
#read in the data as a tsibble
data <- readr::read_csv(file = 'data/data_shipping_and_weather_joined_cleaned.csv') %>%
  mutate(yw = yearweek(yw)) %>%
  select(-X1) %>%
  as_tsibble(key = c(Mode,ORegionDAT, DRegionDAT), index = yw) 

head(data)

autoplot(data, sanitized_cost)
```
# Preliminary correlation visualization

```{r}
data %>%
  filter(Mode=="R" & DRegionDAT =="IL_CHI") %>%
  GGally::ggpairs(columns = 5:9) +
  labs(title = "Chicago R")

data %>%
  filter(Mode=="R" & DRegionDAT =="MA_BOS") %>%
  GGally::ggpairs(columns = 5:9) +
  labs(title = "Boston R")

data %>%
  filter(Mode=="V" & DRegionDAT =="IL_CHI") %>%
  GGally::ggpairs(columns = 5:9) +
  labs(title = "Chicago V")

data %>%
  filter(Mode=="V" & DRegionDAT =="MA_BOS") %>%
  GGally::ggpairs(columns = 5:9) +
  labs(title = "Boston V")
```

Temperature:
* It looks as though R trucking prices correlate positively with temperature (highest correlation with tmax, lower with tavg, yet lower with tmin).
* However, V trucking prices don't really have a correlation with temperature. 


As far as precipitation goes: 
* R trucking prices have a negative correlation with precipitation. However, precipitation and temperature also have a negative correlation, so it's not clear if precipitation actually affects trucking prices, or if it just tends to rain less on hot days when more refrigeration is needed. 
* V trucking prices also have a negative correlation with precipitation, almost as much as R trucking prices do. But V trucking prices don't correlate with temperature. So maybe the precipitation is actually causally affecting prices? Not certain why that would be.



