---
output:
  pdf_document: default
  html_document: default
---
#ARIMA/SARIMA

```{r warning = FALSE, message = FALSE}
library(plyr)
library(fpp3)
library(tsibble)
library(forecast)
library(zoo)
```

```{r}
# Import the interpolated data with diesel
data <- readr::read_csv(file = 'data/Fresno/data_interpolated_with_diesel.csv') %>%
  dplyr::select(-X1) 

# have yet to mutate yw to yearweek type, nor have I made it into a tsibble object yet
```

```{r}
# Only take the necessary columns
data <- data %>%
  dplyr::select(Mode, ORegionDAT, DRegionDAT, tmax, prcp, diesel_price, yw, approx_cost)
```

```{r}
#trim leading and trailing na's
data <- drop_na(data)
```

```{r}
#create training set - up through 2020 of the time series
train <- data %>% 
  dplyr::filter(yw <= "2020 W53") %>%
  mutate(yw = yearweek(yw)) %>%
  as_tsibble(key = c(Mode, ORegionDAT, DRegionDAT), index = yw)

# Make the original data a tsibble now with yearweek index
data <- data %>%
  mutate(yw = yearweek(yw)) %>%
  as_tsibble(key = c(Mode, ORegionDAT, DRegionDAT), index = yw)
```

There are many possible arima models - based on choice of hyperparameters and whether to include seasonality or not. The ARIMA() function automatically chooses the best hyperparameters.
```{r}
fit <- train %>%
  model(ARIMA(approx_cost ~ prcp + tmax + diesel_price))
```
```{r}
#see what the automatically chosen arima models were.
report(fit %>% filter (Mode=="R", DRegionDAT=="IL_CHI"))
report(fit %>% filter (Mode=="V", DRegionDAT=="IL_CHI"))
report(fit %>% filter (Mode=="R", DRegionDAT=="MA_BOS"))
report(fit %>% filter (Mode=="V", DRegionDAT=="MA_BOS"))
```
It looks like for the first 3 time series ARIMA() automatically picked up on the period 52 seasonality. For Boston V data, it did not. Also it chose a different set of hyperparameters for each time series. 

```{r}
#forecast
#in order to produce the forecast of approx_cost, we need to feed in a forecast of tmax, prcp, and diesel_price. Instead of producing a forecast, I will just use the actual data here. 
future_data <- data %>% 
  filter_index("2021 W01"~"2021 W26") %>%
  select(Mode, ORegionDAT, DRegionDAT, yw, tmax, prcp, diesel_price)
fc <- fit %>% forecast(future_data)
```

```{r fig.height = 6, fig.width = 10}
#plot
fc %>%
  autoplot(train) +
  autolayer(data, colour = "black") +
  labs(title="SARIMA")
```

#Looking at fitted values and residuals

```{r}
#get fitted values and residuals
aug = augment(fit)
```

```{r fig.height = 3, fig.width = 8}
#autoplot them
autoplot(aug, .innov) +
  labs(title = "Residuals from the ARIMA/SARIMA model")
```

```{r}
#histograms
aug %>%
  ggplot(aes(x = .innov)) +
  geom_histogram() +
  facet_grid(rows = vars(Mode), cols = vars(DRegionDAT)) +
  labs(title = "Histograms of residuals")
```

```{r}
#acf
aug %>%
  ACF(.innov, lag_max = Inf) %>%
  autoplot() +
  facet_grid(rows = vars(Mode), cols = vars(DRegionDAT)) +
  labs(title = "ACF of Residuals")
```

## Looking at forecast errors

```{r}
accuracy(fc, data)
```

