---
output:
  pdf_document: default
  html_document: default
---
# Data Cleaning

The goal of this script is to combine the diesel data into the rest of the aggregated data in order to add another column. 

```{r message = FALSE, warning = FALSE}
# Load packages
library(tidyverse)
library(plyr)
library(dplyr)
library(tsibble)
library(ggplot2)
library(feasts)
library(lubridate)
library(janitor)
```

```{r}
# read shipping cost time series data
data_raw <- readr::read_csv('data/data_interpolated.csv') %>%
  select(-X1) %>%
  mutate(yw = yearweek(yw)) %>%
  as_tsibble(key = c(Mode, DRegionDAT, ORegionDAT), index = yw) %>%
  arrange(yw)

data_raw
```

```{r}
# Loading the weather data, specifying the data types being imported.

diesel_raw <- read_csv('data/diesel_weekly_prices.csv')

head(diesel_raw)
```

```{r}
# Custom function to convert the date from diesel to standard

convert_yearweek <- function(chr){
  month = substr(chr, 1, 3)
  day = substr(chr, 5, 6)
  year = substr(chr, 9, 12)
  output = paste(day,"-",month,"-",year, sep = "")
  return(output)
}

# Test case
convert_yearweek("Jan 21, 2021")
```

## yearweek date format

Let's convert the date information to a yearweek format.
```{r}
# convert date to yearweek and add a column for yearweek 
require(zoo)
diesel_yw <- diesel_raw %>%
  mutate(Date = as.Date(Date, format="%d-%b-%y")) %>%
  mutate(yw = yearweek(Date))
  
head(diesel_yw)
```

## Drop Date data

```{r}
diesel_yw <- diesel_yw %>%
  select(-Date) %>%
  as_tsibble(index = yw)

```

# Join the weekly diesel and shipping data into one data set

```{r}
diesel_yw

data_raw

data_all = join(data_raw, diesel_yw, by = "yw", type = "left", match = "all") %>%
              as_tsibble(key = c(Mode, DRegionDAT),
              index = yw)

data_all
```

I want to plot the `cost`, `precip`, and `temp` data all together to see if I notice any visual patterns. I'll normalize all the values first so that the plot looks alright

Normalize
```{r}
scaled_data <- data_all %>% 
  mutate_at(c("sanitized_cost", "prcp", "tavg", "tmax", "tmin", "diesel_price"), ~(scale(.) %>% as.vector))

head(scaled_data)
```

Plot normalized shipping cost (green), precip (blue), and tavg (black) for each combination of mode/destination.

```{r}
ggplot() + 
  geom_line(data = filter(scaled_data, DRegionDAT=="IL_CHI" & Mode == "R"), aes(x = yw, y = tavg), color = "black") +
  geom_line(data = filter(scaled_data, DRegionDAT=="IL_CHI" & Mode == "R"), aes(x = yw, y = prcp), color = "blue") +
  geom_line(data = filter(scaled_data, DRegionDAT=="IL_CHI" & Mode == "R"), aes(x = yw, y = sanitized_cost), color = "green") +
  geom_line(data = filter(scaled_data, DRegionDAT=="IL_CHI" & Mode == "R"), aes(x = yw, y = diesel_price), color = "red") +
  labs(title = "Chicago Refrigerated", y= "normalized value")

ggplot() + 
  geom_line(data = filter(scaled_data, DRegionDAT=="MA_BOS" & Mode == "R"), aes(x = yw, y = tavg), color = "black") +
  geom_line(data = filter(scaled_data, DRegionDAT=="MA_BOS" & Mode == "R"), aes(x = yw, y = prcp), color = "blue") +
  geom_line(data = filter(scaled_data, DRegionDAT=="MA_BOS" & Mode == "R"), aes(x = yw, y = sanitized_cost), color = "green") +
  labs(title = "Boston Refrigerated", y= "normalized value")

ggplot() + 
  geom_line(data = filter(scaled_data, DRegionDAT=="IL_CHI" & Mode == "V"), aes(x = yw, y = tavg), color = "black") +
  geom_line(data = filter(scaled_data, DRegionDAT=="IL_CHI" & Mode == "V"), aes(x = yw, y = prcp), color = "blue") +
  geom_line(data = filter(scaled_data, DRegionDAT=="IL_CHI" & Mode == "V"), aes(x = yw, y = sanitized_cost), color = "green") +
  labs(title = "Chicago Van", y= "normalized value")

ggplot() + 
  geom_line(data = filter(scaled_data, DRegionDAT=="MA_BOS" & Mode == "V"), aes(x = yw, y = tavg), color = "black") +
  geom_line(data = filter(scaled_data, DRegionDAT=="MA_BOS" & Mode == "V"), aes(x = yw, y = prcp), color = "blue") +
  geom_line(data = filter(scaled_data, DRegionDAT=="MA_BOS" & Mode == "V"), aes(x = yw, y = sanitized_cost), color = "green") +
  labs(title = "Boston Van", y= "normalized value")
```

## Save the cleaned up and joined data set to a csv file.
```{r}
write.csv(data_all, "data/data_interpolated_with_diesel.csv")
```

