Clustering of weather in Monterey

```{r message = FALSE, warning = FALSE}
# Load packages
library(fpp3)
library(tsibble)
library(plyr)
library(dplyr)
library(tidyverse)
library(ggplot2)
```

```{r, warning = FALSE, message = FALSE}
# Import weather data
weather <- readr::read_csv(file = 'data/Monterey_weather_lags.csv') %>%
  dplyr::select(-X1) %>%
  mutate(yw = yearweek(yw)) %>%
  relocate(yw) %>%
  as_tsibble(index = yw)
```

Get data into right format for clustering
```{r}
weather1 <- weather %>%
  as.data.frame() %>%
  dplyr::select(yw, tmax, prcp_lag4, tmax_lag4) %>% # lagging by 4 per Grace's suggestion
  drop_na()

row.names(weather1) <- as.character(weather1$yw)
weather1 <- weather1 %>% dplyr::select(-yw)
```

Interactive visualizations to play around with to see how the prices of different lettuce types relate to each other.

```{r}
library(plotly) 
```

```{r}
weather1_plot <- weather1 %>% mutate(yw = row.names(weather1))

weather1_plot

p <- ggplot(weather1_plot, aes(x=log(tmax), y=log(prcp_lag4), 
                       color = format(as.Date(yearweek(yw)),format = "%Y"), 
                       text=yw)) +
  geom_point(alpha=0.75)

ggplotly(p, tooltip="yw")
```

library for PCA and clustering visualizations to come.
```{r}
library(factoextra)
```

We can make a cool 3D interactive plot for the three weather variables being used.
```{r}
library(rgl)
# 3D plot (window pops out)
plot3d(weather1$tmax, weather1$prcp_lag4, weather1$tmax_lag4)
```

# K-Means clustering
```{r}
comps <- weather1

# Determine number of clusters
wss <- (nrow(comps)-1)*sum(apply(comps,2,var))
for (i in 2:8) wss[i] <- sum(kmeans(comps, 
                                     nstart = 25, 
                                     iter.max=1000,
                                     centers=i)$withinss)
plot(1:8, wss, type="b", xlab="Number of Clusters",
     ylab="Within groups sum of squares")
```
I don't see an obvious elbow bend in the plot (same thing that happened with Grace's clustering after performing PCA on lettuce data), so it's not clear to me how many clusters to do. I'll try a few possibilities. 

For $k$ clusters, we can perform the same set of steps:

```{r}
# Perform the clustering
cluster_k <- function(k) {
  
  # set seed for reproducibility
  set.seed(123) 
  
  # do the clustering
  clusterk <- kmeans(comps, k, nstart = 25, iter.max=1000)
  
  # 3D plot
  plot3d(comps$tmax, comps$prcp_lag4, comps$tmax_lag4, col=clusterk$clust)
  
  # print sizes of the clusters
  print(sort(table(clusterk$clust)))
  
  return(clusterk)
}

# Convert to data.frame
df_the_cluster <- function(data, clustering, k) {
  
  # sort names
  clust <- names(sort(table(clustering$clust)))

  # allocate list of size k to be filled with each cluster's data.frame
  clusters_df = vector("list", k)
  
  # loop over each cluster
  for(i in 1:k) {
    cluster = row.names(data[clustering$clust==clust[i],])
    
    # turn the cluster into a data.frame to be labeled
    clusters_df[[i]] <- data.frame(cluster) %>%
      rename(yw = cluster) %>%
      mutate(yw = yearweek(yw)) %>%
      mutate(cluster = i)
  }
  
  # initialize full data.frame
  cluster_df = clusters_df[[1]]
  
  # join the rest of the data.frames
  for(i in 2:k) {
    cluster_df = join(cluster_df, clusters_df[[i]], type = "full", by = c("yw", "cluster"))
  }
  
  # clean up, make tsibble
  cluster_df <- cluster_df %>%
    mutate(cluster = as.character(cluster)) %>%
    as_tsibble(index = yw)
  
  return(cluster_df)
}

# Produce the plot
picture <- function(cluster_df) {
  
  # plot the clusters all together over time
  ggplot(cluster_df, aes(x=yw, y=0, color = cluster)) + geom_point()
}
```

First, I'll do 2 clusters.

```{r}
k = 2
clustering2 <- cluster_k(k)
clustering2_df <- df_the_cluster(weather1, clustering2, k)
picture(clustering2_df)
```

Next, let's try 3 clusters.

```{r}
k = 3
clustering3 <- cluster_k(k)
clustering3_df <- df_the_cluster(weather1, clustering3, k)
picture(clustering3_df)
```

Next, let's try 4-10 clusters.

```{r}
k = 4
clustering4 <- cluster_k(k)
clustering4_df <- df_the_cluster(weather1, clustering4, k)
picture(clustering4_df)

k = 5
clustering5 <- cluster_k(k)
clustering5_df <- df_the_cluster(weather1, clustering5, k)
picture(clustering5_df)

k = 6
clustering6 <- cluster_k(k)
clustering6_df <- df_the_cluster(weather1, clustering6, k)
picture(clustering6_df)

k = 7
clustering7 <- cluster_k(k)
clustering7_df <- df_the_cluster(weather1, clustering7, k)
picture(clustering7_df)
```
Let's try doing a clustering of $k = 6$. 

```{r}
clustering_choice = clustering6_df

new_weather <- weather %>% 
  drop_na() %>%
  mutate(cluster1 = ifelse(yw %in% (clustering_choice %>% as_tibble() %>% filter(cluster == 1) %>% pull(yw)), 1, 0)) %>%
  mutate(cluster2 = ifelse(yw %in% (clustering_choice %>% as_tibble() %>% filter(cluster == 2) %>% pull(yw)), 1, 0)) %>%
  mutate(cluster3 = ifelse(yw %in% (clustering_choice %>% as_tibble() %>% filter(cluster == 3) %>% pull(yw)), 1, 0)) %>%
  mutate(cluster4 = ifelse(yw %in% (clustering_choice %>% as_tibble() %>% filter(cluster == 4) %>% pull(yw)), 1, 0)) %>%
  mutate(cluster5 = ifelse(yw %in% (clustering_choice %>% as_tibble() %>% filter(cluster == 5) %>% pull(yw)), 1, 0)) %>%
  mutate(cluster6 = ifelse(yw %in% (clustering_choice %>% as_tibble() %>% filter(cluster == 6) %>% pull(yw)), 1, 0))

new_weather

new_weather %>% write.csv("data/weather_clustered.csv")
```




